Regular singular Volterra equations on complex domains

### 2023-07-29 reg-sing-volterra.tex
Veronica add changes according to the gray items of brainstorming

@@

@@

Since $\softpart$ is a holomorphic Volterra operator, $\softker$ is a holomorphic function on $\domain^2$. We'll allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we won't allow any sharper singularity. We'll also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$. Altogether, we'll require:
\begin{itemize}
\condconst{diag}{\epsilon, \lambda_\Delta}\label{cond:eps-lambda} We have
\[ \big| k_\text{extra} (a, a') \big| \lesssim \textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain$.
\end{itemize}
Notice that this condition prevents $\softker$ from being separable---unless it's zero, of course.
\color{RoyalBlue}
Our ultimate goal is the study of certain integral equations where the integral kernel is a perturbation of $k_\text{basic}$. In particular, we are interested in holomorphic Volterra operators $\volterra=\hardpart+\softpart$, hence the kernel $k_\text{extra}$ of $\softpart$ is a holomorphic function on $\Omega^2$.

For some of our results, we need to keep $k_\text{ext}$ under control at two different regimes: close to the point $\zeta=0$ and far toward infinity. In the former case, we require $k_\text{extra}$ to grow as $|\zeta|^{\epsilon-1}$ for some positive constant $\epsilon$; in the latter, we require $k_\text{ext}$ to be exponentially bounded
\begin{itemize}
\condconst{bounds}{\epsilon, \lambda}%%\label{cond:eps-lambda} (remove line break)
for every $a,a'\in\Omega$
\[ \big| k_\text{extra} (a, a') \big|\le C_{k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} e^{\lambda|\zeta(a)-\zeta(a')|}\]
\end{itemize}

Notice that if $a$ and $a'$ are close to $\zeta=0$, then the exponential factor is bounded and $k_\text{extra}(a,a')$ goes like $|\zeta(a)|^{\epsilon-1}$. Conversely, as $|\zeta(a)|$ goes to infinity (far from $\zeta=0$), the exponential term will be dominant because the polynomial growth of $|\zeta(a)|^{\epsilon-\tau}$ can be bounded by $e^{|\zeta(a)|}$.
\color{black}
\subsection{Main results}
%%\begin{defn}\label{fin-order}
%%Consider a Volterra operator $\mathcal{V}$ of the form
%%\[ [\mathcal{V}\varphi](a) = m(a)\,\varphi(a) + \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta. \]
%%We'll say $\mathcal{V}$ is {\em effectively finite-order} over a domain $\Omega$ if there are some $c, c' \in (0, \infty)$ for which
%%\begin{itemize}
%%\item $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$
%%\item $|k(a, a')| \lesssim e^{c|\zeta(a)| + c'|\zeta(a')|}$ over all $a, a' \in \Omega$
%%\end{itemize}
%%and at one of the following holds:
%%\begin{enumerate}
%%\item\label{case:0th-order} $m$ isn't the zero function.
%%\item\label{case:pos-order} $m$ is the zero function, and there's some $\lambda \in (0, \infty)$ for which
%%\[ |k(a, a')| \in O_\text{\rm diag}\big( |\zeta(a) - \zeta(a')|^{\lambda-1} \big), \]
%%where {\rm ``diag''} means the diagonal in $\Omega^2$.
%%\end{enumerate}
%%We'll say $\mathcal{V}$ has order $0$ in case~\ref{case:0th-order}, and order at least $\lambda$ in case~\ref{case:pos-order}.
%%\end{defn}
\begin{thm}\label{thm:basic_volterra}
Let $\hardpart$ be the operator described in Section~\ref{setting:basic} and assume it satisfies {\em Condition \eqref{cond:sing}}. Then the regular singular Volterra equation
\[ f = \hardpart f \]
have the {\em prototype solution}
\begin{equation}\label{eqn:test_solution}
f_0(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
\end{equation}
Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.

@@

%%The solution $f_0$ scales like $\zeta^{\tau-1}$ as $\zeta$ goes to zero. To be precise, as $\zeta$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.
\end{thm}
\begin{proof}
Section~\ref{sec:proto-construction-regularity}. Proposition~\ref{prop:construction} shows that $f_0$ is a solution, and Proposition~\ref{prop:asymptotic at zero} shows that it scales as desired as $\zeta$ goes to zero.
\end{proof}
\begin{rmk}
If $q$ has a limit at $\zeta = 0$, the solution $f_0$ from Theorem~\ref{thm:basic_volterra} can be written as a constant mutiple of $\zeta^{\tau-1}$ plus a function which is $O(\zeta^\tau)$ at $\zeta = 0$.

\textcolor{RoyalBlue}{$f_0 \in F\zeta^{\tau-1} + O(\zeta^\tau)$ near $\zeta = 0$ for some non-zero constant $F$.}
\end{rmk}
\begin{thm}\label{thm:proto-growth}
Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}} and {\em \eqref{cond:slow}} from Section~\ref{setting:basic}. Then the solution $f_0$ from {\em Theorem~\ref{thm:basic_volterra}} is uniformly of exponential type $\lambda_0$ \textcolor{orange}{[explain what we mean by ``uniformly''---for example, by mentioning the discussion in Section~\ref{sec:fn-space-defs}, including the footnote]}. In light of the behavior at $\zeta = 0$ described above, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{thm}
\begin{lemma}\label{thm:perturbed_volterra}
Let $g$ be a function in the space $\in\singexp{\sigma+\epsilon}{A}(\Omega)$ defined in Section~\ref{fn-spaces}. The Volterra equation
\[ f = \Big[\hardpart +\softpart \Big] f + g \]
given by an operator of the kind described in Sections \ref{setting:basic} and \ref{setting:perturbed}, admits a unique solution $f$ that belongs to $\singexp{\sigma+\epsilon}{\Lambda}(\Omega)$, for every $\Lambda\geq A$ \textcolor{magenta}{[check]}. 
\end{lemma}

\begin{thm}\label{thm:general_volterra}
    Assume $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}, \eqref{cond:slow}} and {\em \eqref{cond:diag-basic}} from Section \ref{setting:basic}. Assume $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section \ref{setting:perturbed}. Then the Volterra equation 
    \[f = \left[ \hardpart + \softpart \right] f\]
    admits a unique solution in the affine subspace
\[ f_0 + \singexp{\tau-1+\epsilon}{{\Lambda}}(\Omega) \]
of the function space $\singexp{\tau-1}{{\Lambda}}(\Omega)$, defined in Section~\ref{fn-spaces}, for $\Lambda$ ``big enough'' (meaning $\Lambda>\lambda_\Delta$, and we may require $\Lambda \gg \lambda_\Delta$). The function $f_0$ is the prototypical solution of \eqref{eqn:test_solution} and it belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.
\end{thm}
%%\begin{thm}
%%Let $\Omega$ be an acute-angled sector around $0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.}

@@

\begin{enumerate}
\item[$\bullet$] $P$ is a monic degree-$d$ polynomial with only simple zeros; 
\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha_j)\neq 0$ for all $j=1,...,d$;
\item[$\bullet$] $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, for every $|z|>A$
\[ R_r(z^{-1}) = \sum_{j=0}^\infty R_{r,j} z^{-j}. \]
\end{enumerate}

@@

\begin{lemma}
 For every $j=1,...,d$, let $\hat{P}_j$ be the Volterra operator

\begin{equation}\label{P-hat_j}
\hat{P}_j:=P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^r
\end{equation}

If $\hat{\psi}_j$ is a solution of $\hat{P}_j\hat{\psi}_j=0$ then its Laplace transform $\Psi_j:=\laplace_{\zeta,\alpha_j}^{\theta}\hat{\psi}_j$, defined for a suitable direction $\theta$, is a solution of $\mathcal{P}\Psi_j=0$. By suitable direction we mean that the ray $\Gamma_{\alpha_j}^\theta$ must be contained in the domain $\Omega_j$. \footnote{We use the shorthand notation $\Omega_j$ for $\Omega_{\alpha_j}$} In particular, $\Omega_j$ does not contain the tubolar neighbourhood of all the other critical points toward infinity as drawn in Section \ref{setting:domain}.      
\end{lemma}

@@

    \begin{align*}
        \mathcal{P}\Psi_j&=\mathcal{P}\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{\psi}_j\\
        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\hat{\psi}_j\\
        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{P}_j\hat{\psi}_j
    \end{align*}
\end{proof}

We can now state and prove the main result of this section, namely that the Volterra operator $\hat{P}_j$ admits a unique solution $\hat{\psi}_j$ %in the function space $(\zeta-\alpha_j)^{\tau_j}+\singexp{\tau_j}{\lambda}(\Omega_j)$.

\begin{thm}\label{thm:example}
    There exists a unique solution of $\hat{P}_j\hat{\psi}_j=0$ such that 
    \[\hat{\psi}_j = f_{0,j}+ f_j\]

    where $f_{0,j}$ scales like $\zeta^{\tau_j-1}$ as $\zeta$ goes to $\alpha_j$ and $f_j\in\singexp{\tau_j}{\Lambda}(\Omega_j)$ for $\Lambda$ ``big enough'' (meaning $\Lambda>2A$, and we may require $\Lambda \gg 2A$). The result holds for every $j=1,...,d$. 
\end{thm}

\begin{proof}
\textcolor{orange}{One option: ``Let $p = P(-\zeta)$ and $q = Q(-\zeta)$, as written in commented-out line. Another: $P(-\zeta(a)) = \int_{\zeta = \alpha}^{\zeta(a)}$}

First of all, we rewrite $\hat{P}_j\varphi=0$ as $\varphi = \volterra_j \varphi $: %we introduce the notation $p(a):=P(-\zeta(a))$ and $q(a)=Q(-\zeta(a))$, then $\hat{P}_j$ is

\begin{align*}
    -P(-\zeta)\varphi= \int_{\zeta=\alpha_j}^\zeta Q(-\zeta')  \, \varphi \, d\zeta' + \int_{\zeta=\alpha_j}^\zeta k_R(\zeta,\cdot)  \, \varphi \, d\zeta
\end{align*}
with \[k_R(a,a')=\sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{R_{r,j}}{j!} \, (\zeta(a)-\zeta(a'))^{j+1} \, (-\zeta(a'))^r\]

@@

\begin{align}
   \nonumber \varphi& =-\int_{\zeta=\alpha_j}^\zeta \frac{Q(-\zeta')}{P(-\zeta)}  \, \varphi \, d\zeta' - \int_{\zeta=\alpha_j}^\zeta \frac{k_R(\zeta,\cdot)}{P(-\zeta)}  \, \varphi \, d\zeta' \\
   \nonumber \varphi& = \hardpart^j \, \varphi+ \softpart^j \, \varphi \\
   \varphi &= \volterra^j \, \varphi
\end{align}

Notice that $\hardpart^j$ is holomorphic and separable, while $\softpart^j$ is holomorphic and non-separable. In addition, $\hardpart^j$ is of the type defined in Section \ref{setting:basic} and it satisfies Condition \eqref{cond:sing}: by Taylor expanding the polynomials $P$ and $Q$ at $-\alpha_j$

\begin{align*}
    -\frac{Q(-\zeta')}{P(-\zeta)}&=-\frac{Q(-\alpha_j)+q_1(\zeta'-\alpha_j)+q_2 (\zeta'-\alpha_j)^2+...}{P'(-\alpha_j)(-\zeta+\alpha_j)+ p_2 (\zeta-\alpha_j)^2+p_3(\zeta-\alpha_j)^3+...}\\
    &=\frac{Q(-\alpha_j)}{P'(-\alpha_j)(\zeta-\alpha_j)}\frac{1+q_1'(\zeta'-\alpha_j)+q_2' (\zeta'-\alpha_j)^2+...}{1+ p_2' (\zeta-\alpha_j)+p_3'(\zeta-\alpha_j)^2+...}\\
    &=\frac{Q(-\alpha_j)}{P'(-\alpha_j)(\zeta-\alpha_j)}\frac{1+q_1'(\zeta'-\alpha_j)+q_2' (\zeta'-\alpha_j)^2+...}{1+p_2' (\zeta-\alpha_j)+p_3'(\zeta-\alpha_j)^2+...}
\end{align*}
hence setting $\tau_j:=\frac{Q(-\alpha_j)}{P'(-\alpha_j)}$, we find

\begin{equation*}
    -\frac{Q(-\zeta')}{P(-\zeta)}-\frac{\tau_j}{\zeta-\alpha_j}
\end{equation*}
is bounded as $\zeta'$ and $\zeta$ approach $\alpha_j$.

Then, the proof will follow by Theorem \ref{thm:general_volterra}, once we proved that $\volterra^j$ satisfies the required assumptions.

\begin{enumerate}
    \item[$\bullet$] $\hardpart^j$ satisfies Condition \eqref{cond:slow}: by assumption $P$ and $Q$ are polynomials, and $Q$ has degree less that $P$. Hence for $\zeta$ outside some neighbourhood $U$ of $\zeta=\alpha_j$  
\begin{align*}
    \sup_U \Big\vert \frac{1}{P}\Big\vert =:c_p \qquad\qquad \sup_U \Big\vert\frac{Q}{P}\Big\vert =:\lambda_\text{ration} 
\end{align*}
    and we set $\lambda_0:=\log(c_p)+\lambda_\text{ratio}$. 
    \item[$\bullet$] $\hardpart^j$ satisfies Condition \eqref{cond:diag-basic}: in fact $P$ and $Q$ are polynomials and $Q$ has degree less than $P$, hence their ratio is exponentially bounded if $a,a'$ far from $\alpha_j$. In particular, $\lambda_\Delta=2A$ is a possible choice, where $A$ is the radius of convergence of the functions $R_r$ (see \ref{sec:level 1 ODE}).    
    \item[$\bullet$]  $\softpart^j$ satisfies Condition \eqref{cond:eps-lambda}: recall that all functions $R_r(z^{-1})$ are holomorphic for $|z|>A$,

    \begin{align*}
        \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{| R_{r,j}|}{j!} \, \frac{|\zeta-\zeta'|^j}{P(-\zeta)}|\zeta'|^r  &\leq C \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{A^j}{j!} \, \frac{|\zeta-\zeta'|^{j+1}}{|P(-\zeta)|}|\zeta'|^r \\
        & =C |\zeta-\zeta'| \sum_{r=0}^{d-1} \frac{|\zeta'|^r}{|P(-\zeta)|}\,  e^{A |\zeta-\zeta'|}\\
        &=C |\zeta-\zeta'| \, \Big\vert \frac{Q(-\zeta')}{P(-\zeta)}\Big\vert \sum_{r=0}^{d-1} \frac{|\zeta'|^r}{|Q(-\zeta')|} \, e^{A |\zeta-\zeta'|}\\
        &\leq C_1 |\zeta-\zeta'| \, \Big\vert \frac{Q(-\zeta')}{P(-\zeta)}\Big\vert \,  e^{A |\zeta-\zeta'|}
    \end{align*}
now we notice that $\Big\vert \frac{Q(-\zeta')}{P(-\zeta)}\Big\vert$ is bounded for $\zeta,\zeta'$ far from $\alpha_j$ by the argument we use in the proof of Condition \eqref{cond:diag-basic}. If $\zeta,\zeta'$ are close to $\alpha_j$ we can use Condition \eqref{cond:sing}

\[    \Big\vert \frac{Q(-\zeta')}{P(-\zeta)}\Big\vert  \leq \Big\vert \frac{Q(-\zeta')}{P(-\zeta)} -\frac{\tau_j}{\zeta-\alpha_j}\Big\vert + \frac{\tau_j}{|\zeta-\alpha_j|}\leq C +  \frac{\tau_j}{|\zeta-\alpha_j|} \]

>>>>

\color{gray}

@@

\color{violet}

@@

Since $\softpart$ is a holomorphic Volterra operator, $\softker$ is a holomorphic function on $\domain^2$. We'll allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we won't allow any sharper singularity. We'll also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$. Altogether, we'll require:
\begin{itemize}
\condconst{diag}{\epsilon, \lambda_\Delta}\label{cond:eps-lambda} We have
\[ \big| k_\text{extra} (a, a') \big| \lesssim \textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain$.
\end{itemize}
Notice that this condition prevents $\softker$ from being separable---unless it's zero, of course.

\subsection{Main results}
%%\begin{defn}\label{fin-order}
%%Consider a Volterra operator $\mathcal{V}$ of the form
%%\[ [\mathcal{V}\varphi](a) = m(a)\,\varphi(a) + \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta. \]
%%We'll say $\mathcal{V}$ is {\em effectively finite-order} over a domain $\Omega$ if there are some $c, c' \in (0, \infty)$ for which
%%\begin{itemize}
%%\item $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$
%%\item $|k(a, a')| \lesssim e^{c|\zeta(a)| + c'|\zeta(a')|}$ over all $a, a' \in \Omega$
%%\end{itemize}
%%and at one of the following holds:
%%\begin{enumerate}
%%\item\label{case:0th-order} $m$ isn't the zero function.
%%\item\label{case:pos-order} $m$ is the zero function, and there's some $\lambda \in (0, \infty)$ for which
%%\[ |k(a, a')| \in O_\text{\rm diag}\big( |\zeta(a) - \zeta(a')|^{\lambda-1} \big), \]
%%where {\rm ``diag''} means the diagonal in $\Omega^2$.
%%\end{enumerate}
%%We'll say $\mathcal{V}$ has order $0$ in case~\ref{case:0th-order}, and order at least $\lambda$ in case~\ref{case:pos-order}.
%%\end{defn}
\begin{thm}\label{thm:basic_volterra}
Let $\hardpart$ be the operator described in Section~\ref{setting:basic} and assume it satisfies {\em Condition \eqref{cond:sing}}. Then the regular singular Volterra equation
\[ f = \hardpart f \]
have the {\em prototype solution}
\begin{equation}\label{eqn:test_solution}
f_0(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
\end{equation}
Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.

@@

%%The solution $f_0$ scales like $\zeta^{\tau-1}$ as $\zeta$ goes to zero. To be precise, as $\zeta$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.
\end{thm}
We'll prove this result in Section~\ref{sec:proto-construction-regularity}: by Proposition~\ref{prop:construction} we show that $f_0$ is a solution, and by Proposition~\ref{prop:asymptotic at zero} we show that it scales as desired as $\zeta$ goes to zero.

\begin{rmk}
If $q$ has a limit at $\zeta = 0$, the solution $f_0$ from Theorem~\ref{thm:basic_volterra} can be written as a constant mutiple of $\zeta^{\tau-1}$ plus a function which is $O(\zeta^\tau)$ at $\zeta = 0$.

\textcolor{RoyalBlue}{$f_0 \in F\zeta^{\tau-1} + O(\zeta^\tau)$ near $\zeta = 0$ for some non-zero constant $F$.}
\end{rmk}
\begin{thm}\label{thm:proto-growth}
Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}} and {\em \eqref{cond:slow}} from Section~\ref{setting:basic}. Then the solution $f_0$ from {\em Theorem~\ref{thm:basic_volterra}} is uniformly of exponential type $\lambda_0$ \textcolor{orange}{[explain what we mean by ``uniformly''---for example, by mentioning the discussion in Section~\ref{sec:fn-space-defs}, including the footnote]}. In light of the behavior at $\zeta = 0$ described above, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{thm}

We'll prove this result in Section~\ref{sec:proto-construction-regularity}, Proposition~\ref{prop:asymptotic at infinity}.

\begin{lemma}\label{thm:perturbed_volterra}
Let $g$ be a function in the space $\in\singexp{\sigma+\epsilon}{A}(\Omega)$ defined in Section~\ref{fn-spaces}. The Volterra equation
\[ f = \Big[\hardpart +\softpart \Big] f + g \]
given by an operator of the kind described in Sections \ref{setting:basic} and \ref{setting:perturbed}, admits a unique solution $f$ that belongs to $\singexp{\sigma+\epsilon}{\Lambda}(\Omega)$, for every $\Lambda\geq A$ \textcolor{magenta}{[check]}. 
\end{lemma}

We'll prove this result in Section~\ref{sec:V is a contraction}: in Proposition \ref{prop:get-contraction} we construct the functions space where $\volterra$ is a contraction. Then the result follows by the contraction mapping theorem.

\begin{thm}\label{thm:general_volterra}
    Assume $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}, \eqref{cond:slow}} and {\em \eqref{cond:diag-basic}} from Section \ref{setting:basic}. Assume $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section \ref{setting:perturbed}. Then the Volterra equation 
    \[f = \left[ \hardpart + \softpart \right] f\]
    admits a unique solution in the affine subspace
\[ f_0 + \singexp{\tau-1+\epsilon}{{\Lambda}}(\Omega) \]
of the function space $\singexp{\tau-1}{{\Lambda}}(\Omega)$, defined in Section~\ref{fn-spaces}, for $\Lambda$ ``big enough'' (meaning $\Lambda>\lambda_\Delta$, and we may require $\Lambda \gg \lambda_\Delta$). The function $f_0$ is the prototypical solution of \eqref{eqn:test_solution} and it belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.
\end{thm}

We'll prove this result in Sections~\ref{sec:existence and uniqueness}: by Proposition \ref{prop:smoothing} we show that $\softpart$ maps the prototype solution into a more regular function space. Then the result follows as a consequence of Lemma \ref{thm:perturbed_volterra}.

%%\begin{thm}
%%Let $\Omega$ be an acute-angled sector around $0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.}

@@

\begin{enumerate}
\item[$\bullet$] $P$ is a monic degree-$d$ polynomial with only simple zeros; 
\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial and it does not vanish at the critical point of $P$;
\item[$\bullet$] $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, for every $|z|>A$
\[ R_r(z^{-1}) = \sum_{j=0}^\infty R_{r,j} z^{-j}. \]
\end{enumerate}

@@

\begin{lemma}
 For every root of $P$, let $\hat{P}_{\alpha}$ be the Volterra operator

\begin{equation}\label{P-hat_j}
\hat{P}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha}^{-1})\circ (-\zeta)^r
\end{equation}

If $\hat{\psi}_\alpha$ is a solution of $\hat{P}_\alpha\hat{\psi}_\alpha=0$ then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\hat{\psi}_\alpha$, defined for a suitable direction $\theta$, is a solution of $\mathcal{P}\Psi_\alpha=0$. By suitable direction, we mean that the ray $\Gamma_{\alpha}^\theta$ must be contained in the domain $\Omega_{\alpha}$. \footnote{The domain $\Omega_{\alpha}$ does not contain the tubular neighborhood of all the other critical points toward infinity as drawn in Section \ref{setting:domain}}.      
\end{lemma}

@@

    \begin{align*}
        \mathcal{P}\Psi_\alpha&=\mathcal{P}\laplace_{\zeta,\alpha}^{\theta}\hat{\psi}_\alpha\\
        &=\laplace_{\zeta,\alpha}^{\theta}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\hat{\psi}_j\\
        &=\laplace_{\zeta,\alpha}^{\theta}\hat{P}_\alpha\hat{\psi}_\alpha
    \end{align*}
\end{proof}

We can now state and prove the main result of this section, namely that the Volterra operator $\hat{P}_\alpha$ admits a unique solution $\hat{\psi}_\alpha$. %in the function space $(\zeta-\alpha_j)^{\tau_j}+\singexp{\tau_j}{\lambda}(\Omega_j)$.

\begin{thm}\label{thm:example}
    There exists a unique solution of $\hat{P}_\alpha\hat{\psi}_\alpha=0$ such that 
    \[\hat{\psi}_\alpha = f_{0,\alpha}+ f_\alpha\]

    where $f_{0,\alpha}$ scales like $\zeta^{\tau_\alpha-1}$ as $\zeta$ goes to $\zeta(\alpha)$ and $f_\alpha\in\singexpalg{\tau_\alpha}(\Omega_\alpha)$. The result holds for every critical point of $P$. 
\end{thm}

\begin{proof}
Let $p = P(-\zeta)$ and $q = Q(-\zeta)$ and let $\alpha$ be a simple root of $p$. Hence, by assumptions that $p(\zeta=\alpha)=0$, $p'(\zeta=\alpha)\neq 0$ and $q(\zeta=\alpha)\neq 0$.

First of all, we rewrite $\hat{P}_{\alpha}\varphi=0$ as $\varphi = \volterra_\alpha \varphi $: %we introduce the notation $p(a):=P(-\zeta(a))$ and $q(a)=Q(-\zeta(a))$, then $\hat{P}_j$ is

\begin{align*}
    -\big[ p\, \varphi \big](a)= \int_{\zeta=\alpha}^a q  \, \varphi \, d\zeta' + \int_{\zeta=\alpha}^a k_R(a,\cdot)  \, \varphi \, d\zeta
\end{align*}
with \[k_R(a,a')=\sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{R_{r,j}}{j!} \, (\zeta(a)-\zeta(a'))^{j+1} \, (-\zeta(a'))^r\]

@@

\begin{align}
   \nonumber \varphi (a)& =-\int_{\zeta=\alpha}^a \frac{q}{p(\zeta(a))}  \, \varphi \, d\zeta' - \int_{\zeta=\alpha}^a \frac{k_R(a,\cdot)}{p(\zeta(a))}  \, \varphi \, d\zeta' \\
   \nonumber \varphi (a)& =\Big[ \hardpart^\alpha \, \varphi \Big](a)+ \Big[\softpart^\alpha \, \varphi\Big](a) \\
   \varphi(a) &=\Big[ \volterra^j \, \varphi \Big](a)
\end{align}

Notice that $\hardpart^\alpha$ is holomorphic and separable, while $\softpart^\alpha$ is holomorphic and non-separable. In addition, $\hardpart^\alpha$ is of the type defined in Section \ref{setting:basic} and it satisfies Condition \eqref{cond:sing}: by Taylor expanding the polynomials $p$ and $q$ at $\alpha$

\begin{align*}
    -\frac{q}{p(\zeta(a))}&=-\frac{q(\zeta(\alpha))+c_1(\zeta'-\zeta(\alpha))+c_2 (\zeta'-\zeta(\alpha))^2+...}{-p'(\zeta(\alpha))(\zeta(a)-\zeta(\alpha))+ b_2 (\zeta(a)-\zeta(\alpha))^2+b_3(\zeta(a)-\zeta(\alpha))^3+...}\\
    &=\frac{q\zeta(\alpha))}{p'(\zeta(\alpha))(\zeta(a)-\zeta(\alpha))}\frac{1+c_1'(\zeta'-\zeta(\alpha))+c_2' (\zeta'-\zeta(\alpha))^2+...}{1+ b_2' (\zeta(a)-\zeta(\alpha))+b_3'(\zeta(a)-\zeta(\alpha))^2+...}\\
    &=\frac{q(\zeta(\alpha))}{p'(\zeta(\alpha))(\zeta(a)-\zeta(\alpha))}\frac{1+c_1'(\zeta'-\zeta(\alpha))+c_2' (\zeta'-\zeta(\alpha))^2+...}{1+b_2' (\zeta(a)-\zeta(\alpha))+b_3'(\zeta(a)-\zeta(\alpha))^2+...}
\end{align*}
hence setting $\tau_\alpha:=\frac{q(\zeta(\alpha))}{p'(\zeta(\alpha))}\neq 0$, we find

\begin{equation*}
    -\frac{q(\zeta(a'))}{p(\zeta(a))}-\frac{\tau_\alpha}{\zeta(a)-\zeta(\alpha)}
\end{equation*}
is bounded as $\zeta(a')$ and $\zeta(a)$ approach $\zeta(\alpha)$.

Then, the proof will follow by Theorem \ref{thm:general_volterra}, once we proved that $\volterra^\alpha$ satisfies the required assumptions.

\begin{enumerate}
    \item[$\bullet$] $\hardpart^\alpha$ satisfies Condition \eqref{cond:slow}: by assumption $p$ and $q$ are polynomials, and $q$ has degree less that $p$. Hence for $a$ outside some neighbourhood $U$ of $\alpha$  
\begin{align*}
    \sup_U \Big\vert \frac{1}{p}\Big\vert =:c_p \qquad\qquad \sup_U \Big\vert\frac{q}{p}\Big\vert =:\lambda_\text{ration} 
\end{align*}
    and we set $\lambda_0:=\log(c_p)+\lambda_\text{ratio}$. 
    \item[$\bullet$] $\hardpart^\alpha$ satisfies Condition \eqref{cond:diag-basic}: in fact $p$ and $q$ are polynomials and $q$ has degree less than $p$, hence their ratio is exponentially bounded if $a,a'$ are far from $\alpha$. In particular, $\lambda_\Delta=2A$ is a possible choice, where $A$ is the radius of convergence of the functions $R_r$ (see \ref{sec:level 1 ODE}).    
    \item[$\bullet$]  $\softpart^\alpha$ satisfies Condition \eqref{cond:eps-lambda}: recall that all functions $R_r(z^{-1})$ are holomorphic for $|z|>A$,

    \begin{align*}
        \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{| R_{r,j}|}{j!} \, \frac{|\zeta(a)-\zeta(a')|^j}{p(\zeta(a))}|\zeta(a')|^r  &\leq C \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{A^j}{j!} \, \frac{|\zeta(a)-\zeta(a')|^{j+1}}{|p(\zeta(a))|}|\zeta(a')|^r \\
        & =C |\zeta(a)-\zeta(a')| \sum_{r=0}^{d-1} \frac{|\zeta(a')|^r}{|p(\zeta(a))|}\,  e^{A |\zeta(a)-\zeta(a')|}\\
        &=C |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \sum_{r=0}^{d-1} \frac{|\zeta'|^r}{|q(\zeta(a'))|} \, e^{A |\zeta(a)-\zeta(a')|}\\
        &\leq C_1 |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \,  e^{A |\zeta(a)-\zeta(a')|}
    \end{align*}
now we notice that $\Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert$ is bounded for $a,a'$ far from $\alpha$ by the argument we use in the proof of Condition \eqref{cond:diag-basic}. If $a, a'$ are close to $\alpha$ we can use Condition \eqref{cond:sing}

\[    \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert  \leq \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))} -\frac{\tau_\alpha}{\zeta(a)-\zeta(\alpha)}\Big\vert + \frac{\tau_\alpha}{|\zeta(a)-\zeta(\alpha)|}\leq C +  \frac{\tau_\alpha}{|\zeta(a)-\zeta(\alpha)|} \]
